Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 99)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
                                                          "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 99)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

>>>>

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 1000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
                                                          "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 1000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
